A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2015-11-12 archive/v1/docs/data_v1.01.tex
Started corrections.

\paragraph{Redshift.} [TO DO: WHO???] found from SDSS spectra that J1331 has two redshifts inside 1 arcsec: The smaller one, $z_d = 0.113$, is the redshift of J1331 itself, the larger one, $z_s = 0.254$, is the redshift of the lensed background source \citep{SWELLSIII}. According to its redshift and the WMAP5 [TO DO: Explain?] cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of 1 arcsec $\hat{=}$ 2.01 kpc.

\paragraph{HST imaging.} We use the follow-up HST imaging, with which \citet{SWELLSI} confirmed that J1331 is indeed a strong gravitational lens [TO DO: REALLY???]. They performed high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) and its WF3 CCD chip.  The images we are using are a combination of four exposures with each an exposure of 400s and were drizzled to a pixel scale of 1 pixel = 0.05 arcsec. In particular we use the images in the filters F450W, to identify the positions of the bluish lensing images, and F814W to create a surface brightness MGE model of the reddish bulge (I-band), used in the JAM dynamical modelling.

@@

[TO DO: How to deal with the typo in J1331s name???? SWELLS call it J1331+3638, but its actual coordinates are a1331+3628.]

>>>>

\paragraph{Redshift.} [TO DO: WHO???] found from SDSS spectra that J1331 has two redshifts inside 1 arcsec: The smaller one, $z_d = 0.113$, is the redshift of J1331 itself, the larger one, $z_s = 0.254$, is the redshift of the lensed background source \citep{SWELLSIII}. According to its redshift and the WMAP5 [TO DO: Do I have to explain the Acronym???] cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of 1 arcsec $\hat{=}$ 2.01 kpc.

\paragraph{HST imaging.} We use the follow-up HST imaging, with which \citet{SWELLSI} confirmed that J1331 is indeed a strong gravitational lens [TO DO: Was it actually SWELLS I that confirmed that???]. They performed high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) and its WF3 CCD chip.  The images we are using are a combination of four exposures with each an exposure of 400s and were drizzled to a pixel scale of 1 pixel = 0.05 arcsec. In particular we use the images in the filters F450W, to identify the positions of the bluish lensing images, and F814W to create a surface brightness MGE model of the reddish bulge (I-band), used in the JAM dynamical modelling.

@@

[TO DO: How to deal with the typo in J1331s name???? SWELLS call it J1331+3638, but its actual coordinates are 1331+3628.]

### 2015-11-12 archive/v1/docs/model_JAM_v1.01.tex
Started corrections.

Jeans axisymmetric models (JAM) assume galaxies (a) to be collisionless, i.e. the collisionless Boltzmann equation for the distribution function $f(\vect{x},\vect{v},t)$ has to be satisfied ($\frac{\diff f(\vect{x},\vect{v},t}{\diff t} = 0$), (b) in a steady state ($\frac{\partial}{\partial t} = 0$), (c) axisymmetric (best described in cylindrical coordinates $(R,z,\phi)$ and $\frac{\partial}{\partial \phi} = 0$). From this follow the axisymmetric Jeans equations as the vector-valued first moment of the Boltzmann equation, i.e.

@@

>>>>

\paragraph{JAM modelling.} Jeans axisymmetric models (JAM) assume galaxies (a) to be collisionless, i.e. the collisionless Boltzmann equation for the distribution function $f(\vect{x},\vect{v},t)$ has to be satisfied ($\frac{\diff f(\vect{x},\vect{v},t}{\diff t} = 0$), (b) in a steady state ($\frac{\partial}{\partial t} = 0$), (c) axisymmetric (best described in cylindrical coordinates $(R,z,\phi)$ and $\frac{\partial}{\partial \phi} = 0$). From this follow the axisymmetric Jeans equations as the vector-valued first moment of the Boltzmann equation, i.e.

@@

\paragraph{Including a NFW halo.} As mentioned above, JAM modelling allows to incorporate an invisible matter component in addition to the luminous matter in the form of an MGE. In Section \ref{sec:results_JAM_NFW} we will include a spherical Navarro-Frenck-White (NFW) dark matter halo \citep{Navarro+1995c,NFW96} in the dynamical model. The classical NFW profile has the form
\begin{equation}
\rho_\text{NFW}(r) \propto \frac{1}{\frac{r}{r_s} \left( 1 + \frac{r}{r_s} \right)^2} \label{eq:NFWprofile}
\end{equation}
and two free parameters, the scale length $r_s$ and a parameter describing the total mass of the halo. We will use $v_\text{200}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological critical density $\rho_\text{crit} \equiv (2H^2)/(8\pi G)$, i.e.
\begin{eqnarray*}
M_\text{200} &=& M(<r_{200})\\
\frac{M_{200}}{ \frac 43 \pi r_{200}^3} &=& 200 \rho_\text{crit}(z=0) \\
v_\text{200} &=& \sqrt{\frac{GM_{200}}{r_\text{200}}}
\end{eqnarray*}
with $\rho_\text{crit}(z=0)=1.43 \cdot 10^{-7} M_\odot / \text{pc}^3$ in the WMAP5 cosmology by \citet{WMAP5cosm}. How much the mass is concentrated in the center of the NFW halo is given by the concentration of the NFW halo defined by 
\begin{equation}
c_{200}\equiv r_{200} / r_s. \label{eq:NFW_c}
\end{equation} 
There is a close relation between the concentration and halo mass in simulations \citep{NFW96}. \citet{Maccio08} found this relation for the WMAP5 cosmology \citep{WMAP5cosm} to be
\begin{equation}
\langle \log c_{200} \rangle (M_{200}) = 0.830 - 0.098 \log \left(h \frac{M_{200}}{10^{12} M_\odot} \right) \label{eq:Maccio08}
\end{equation}
(their equation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their Table A2).

### 2015-11-12 archive/v1/docs/results_JAMwithNFW_v1.01.tex
Started corrections.

\subsection{JAM with a NFW Dark Matter Halo} \label{sec:results_JAM_NFW}

\paragraph{Including a NFW halo.} The dynamical modelling attempts in the previous sections suggest that J1331's inner regions have a slightly more roundish and at large radii more massive mass distribution than expected from the distribution of stars alone. A dark matter halo in addition to the stellar component could explain these findings. We therefore proceed by modelling the mass distribution with a) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$), and b) a spherical NFW [TO DO: introduce abbreviation somewhere] dark matter component \citep{Navarro+1995c,NFW96}. In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile
\begin{equation*}
\rho_\text{NFW}(r) \propto 1 / \frac{r}{r_s} \left( 1 + \frac{r}{r_s} \right)^2.
\end{equation*}
The NFW halo has two free parameters, the scale length $r_s$ and a parameter describing the total mass of the halo. We use $v_\text{200}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological [TO DO: how to express this] critical density, i.e.
\begin{eqnarray*}
M_\text{200} &=& M(<r_{200})\\
\frac{M_{200}}{ \frac 43 \pi r_{200}^3} &=& 200 \rho_\text{crit}(z=0) \\
v_\text{200} &=& \sqrt{\frac{GM_{200}}{r_\text{200}}}
\end{eqnarray*}
with $\rho_\text{crit}(z=0)=1.43 \cdot 10^{-7} M_\odot / \text{pc}^3$ in the WMAP5 cosmology by \citet{WMAP5cosm}. How much the mass is concentrated in the center of the NFW halo is given by the concentration of the NFW halo defined by $c_{200}\equiv r_{200} / r_s$. [TO DO: so toll ist das mit der Radiusbenennung noch nicht.????]. There is a close relation between the concentration and halo mass in simulations \citep{NFW96}. \citet{Maccio08} found this relation for the WMAP5 cosmology \citep{WMAP5cosm} to be
\begin{equation}
\langle \log c_{200} \rangle (M_{200}) = 0.830 - 0.098 \log \left(h \frac{M_{200}}{10^{12} M_\odot} \right) \label{eq:Maccio08}
\end{equation}
(their equation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their Table A2).

\paragraph{Modelling.} The full set of fit parameters is $(\Upsilon_\text{I,*},r_s,v_{200},\beta_z)$, where $\beta_z$ is the constant velocity anisotropy parameter (see Section \ref{sec:model_JAM}). We will investigate this parameter space with a MCMC\footnote{The Python code package for \emph{emcee}, a Monte Carlo Markov Chain implementation by \citet{emcee} is available online at \url{http://dan.iel.fm/emcee/current/}. The version from October 2013 was used in this work.} \citep{emcee} and use priors for the halo parameters to guide the fit to a realistic NFW halo shape.
\\\citet{Dutton10} give a relation for halo vs. stellar mass for late-type galaxies. For an Chabrier IMF stellar population they found
\begin{equation*}
y = y_0 \left( \frac{x}{x_0} \right)^\alpha \left[ \frac 12 + \frac 12 \left(\frac{x}{x_0} \right)^\gamma \right]^{(\beta - \alpha)/\gamma},
\end{equation*}
where $x= m_*$ [$M_\odot h^{-2}$] is the stellar mass, $y = \frac{\langle M_{200}\rangle}{m_*}$ and $\langle M_{200}\rangle$ [$M_\odot h^{-2}$] is the mean halo mass. The parameters for the mean and $2\sigma$ error curves for this relation are$\alpha = -0.5\pm0.15$, $\beta = 0$, $\gamma = 1.0$, $\log_{10} x_0 = 10.4$, $\log_{10} {y_0}_{-0.24}^{+0.28}$ \citet{Dutton10}. Using the stellar mass estimate for J1331 from \citet{SWELLSI} $m_* = (1.06 \pm 0.25) \cdot 10^{11} M_\odot$ for the Chabrier IMF estimate [TO DO: introduce somewhere], we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$. The first of the two quoted errors is due to the $2\sigma$ scatter in the relation by \citet{Dutton10}. The second error is the propagated error due to the uncertainty in the stellar mass. We use this as a rough estimate for the halo of J1331 and as Gaussian prior on $v_{200}$, 
\begin{equation*}
p(v_{200}) = \mathscr{N}(200 \text{km/s} ,40 \text{km/s}).
\end{equation*}
\\We also use the concentration vs. halo mass relation by \citet{Maccio08} in Equation \ref{eq:Maccio08} as a prior on the concentration, i.e.
\begin{equation*}
p(\log c_{200} \mid v_{200}) = \mathscr{N}\left(\langle \log c_{200} \rangle (M_{200}) \mid 0.105 \right).
\end{equation*}
\\For the velocity anisotropy parameter $\beta$ we will again employ a uniform prior 
\begin{equation*}
p(\beta) = \mathscr{U}(-0.5,+0.5)
\end{equation*}
to exclude very unrealistic anisotropies. The full prior used is then
\begin{eqnarray*}
&&p(\Upsilon_\text{I,*},r_s,v_{200},\beta) \\
&&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta), 
\end{eqnarray*}
where the factor $1/\ln\left( 10 r_s\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ [TO DO: introduce concentration] to $(v_{200},r_s)$.
\\We restrict the $v_\text{rms}$ fit to a region $R' \lesssim 3.5$ arcsec, approximately within the effective half-light radius $R_\text{eff} = 2.6$ arcsec. We also include the Einstein mass $M(<R_\text{ein}$ with a 10\% error as an additional constraint in the fit. [TO DO: Didn't include the results from the Moster 2010 relation, because they where quite close to the Dutton 2010 relation anyway. Or should I?]

@@

\begin{figure*}
\centering
\begin{subfigure}{\textwidth}
  \centering
  \includegraphics[width=0.8\linewidth]{fig/B4_rms_error_curves.ps}
  \caption{Comparison of the $v_\text{rms}$ data with the best fit JAM models.}
  \label{fig:modelB4_vrms}
\end{subfigure}
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
  \caption{Circular velocity curve.}
  \label{fig:modelB4_vcirc}
\end{subfigure}%
\hspace{.02\textwidth}
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_projmass.ps}
  \caption{Enclosed mass profile.}
  \label{fig:modelB4_enclMass}
\end{subfigure}
\caption{Best fit JAM model including a NFW halo and velocity anisotropy with parameters given in Table \ref{tab:modelB4_bestfit}. The 12 lines shown correspond to the 12 models randomly drawn from the posterior probability distribution and marked as grey diamonds in Figure \ref{fig:modelB4_triangle}. Overplotted are the Einstein radius (red dotted line) and the effective half-light radius (black dotted line). The blue dashed line marks the radius within which the data and model were fitted. \emph{Panel a)} shows the comparison of the symmetrized $v_\text{rms}$ data (solid blue points) with the best fit JAM models including a NFW halo (red solid lines). Also shown is the non-symmetrized data at larger radii (open blue dots) and an extrapolation of the best fit models, using the same model parameters but the I-band surface brightness MGE for the outer regions of J1331 derived from the Ellipse model (red dashed lines). \emph{Panel b)} shows the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and dark matter (grey). [TO DO: Is this really the spherical $r$? I would think it is actually the cylindrical $R$.] \emph{Panel c)} shows the corresponding enclosed mass profile. Overplotted is also the Einstein mass at the Einstein radius with a 10\% error, which was used in the fit as an additional constraint.}
\label{fig:modelB4_models}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.7\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
\caption{Generating the rotation curve from the JAM model with NFW halo and constant velocity anisotropy with the mean parameters in Table \ref{tab:modelB4_bestfit} and with the best fit rotation parameter $\kappa' = 0.76$ in Equation \ref{eq:kappa_profile} (red solid lines). The second velocity moment in the first panel and the first velocity moment in the second panel with the additional fit parameter $\kappa'$ were fitted to the symmetrized data (solid blue points). The velocity dispersion is simply $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$. At larger radii we compare the unsymmetrized data (open blue dots), the gas kinematics from \citet{SWELLSV} (green diamonds) and a JAM model using the same model parameters but the light distribution MGE generated from the Ellipse model in Figure [TO DO: REF FIGURE] as a prediction for the outer regions of J1331 (red dashed lines). The central regions are very well reproduced and we can also greatly predict the rotation curve at larger radii. Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo.}
\label{fig:modelB4_vrot}
\end{figure*}

>>>>

\subsection{JAM with a NFW dark matter halo} \label{sec:results_JAM_NFW}

\paragraph{Including a dark matter halo.} The dynamical modelling attempts in the previous sections suggest that J1331's inner regions have a slightly more roundish and at large radii more massive mass distribution than expected from the distribution of stars alone. A dark matter halo in addition to the stellar component could explain these findings. We therefore proceed by modelling the mass distribution with a) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$), and b) a spherical NFW dark matter component (see Section \ref{sec:model_JAM}) with free parameters halo scale length $r_s$ and circular velocity at the virial radius $v_{200}$. In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile in Equation \ref{eq:NFWprofile}.

\paragraph{Modelling and priors.} The full set of fit parameters is $(\Upsilon_\text{I,*},r_s,v_{200},\beta_z)$, where $\beta_z$ is the constant velocity anisotropy parameter (see Section \ref{sec:model_JAM}). We will investigate this parameter space with a MCMC\footnote{The Python code package for \emph{emcee}, a Monte Carlo Markov Chain implementation by \citet{emcee} is available online at \url{http://dan.iel.fm/emcee/current/}. The version from October 2013 was used in this work.} \citep{emcee} and use priors for the halo parameters to guide the fit to a realistic NFW halo shape.
\\\citet{Dutton10} give a relation for halo vs. stellar mass for late-type galaxies. For a stellar population with a Chabrier IMF they found
\begin{equation*}
y = y_0 \left( \frac{x}{x_0} \right)^\alpha \left[ \frac 12 + \frac 12 \left(\frac{x}{x_0} \right)^\gamma \right]^{(\beta - \alpha)/\gamma},
\end{equation*}
where $x= m_*$ [$M_\odot h^{-2}$] is the stellar mass, $y = \frac{\langle M_{200}\rangle}{m_*}$ and $\langle M_{200}\rangle$ [$M_\odot h^{-2}$] is the mean halo mass. The parameters for the mean and $2\sigma$ error curves for this relation are$\alpha = -0.5\pm0.15$, $\beta = 0$, $\gamma = 1.0$, $\log_{10} x_0 = 10.4$, $\log_{10} {y_0}_{-0.24}^{+0.28}$ \citet{Dutton10}. Using the stellar mass estimate for J1331 from \citet{SWELLSI} $m_* = (1.06 \pm 0.25) \cdot 10^{11} M_\odot$ for the Chabrier IMF estimate, we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$. The first of the two quoted errors is due to the $2\sigma$ scatter in the relation by \citet{Dutton10}. The second error is the propagated error due to the uncertainty in the stellar mass. We use this as a rough estimate for the halo of J1331 and as Gaussian prior on $v_{200}$, 
\begin{equation*}
p(v_{200}) = \mathscr{N}(200 \text{km/s} ,40 \text{km/s}).
\end{equation*}
\\We also use the concentration vs. halo mass relation by \citet{Maccio08} in Equation \ref{eq:Maccio08} as a prior on the concentration, i.e.
\begin{equation*}
p(\log c_{200} \mid v_{200}) = \mathscr{N}\left(\langle \log c_{200} \rangle (M_{200}) \mid 0.105 \right).
\end{equation*}
\\For the velocity anisotropy parameter $\beta$ we will again employ a uniform prior 
\begin{equation*}
p(\beta) = \mathscr{U}(-0.5,+0.5)
\end{equation*}
to exclude very unrealistic anisotropies. The full prior used is then
\begin{eqnarray*}
&&p(\Upsilon_\text{I,*},r_s,v_{200},\beta) \\
&&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta), 
\end{eqnarray*}
where the factor $1/\ln\left( 10 r_s\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ to $(v_{200},r_s)$.
\\We restrict the $v_\text{rms}$ fit to a region $R' \lesssim 3.5$ arcsec, approximately within the effective half-light radius $R_\text{eff} = 2.6$ arcsec. We also include the Einstein mass $M(<R_\text{ein}$ with a 10\% error as an additional constraint in the fit. [TO DO: Didn't include the results from the Moster 2010 relation, because they where quite close to the Dutton 2010 relation anyway. Or should I?]

@@

\begin{figure*}
\centering
\begin{subfigure}{\textwidth}
  \centering
  \includegraphics[width=0.8\linewidth]{fig/B4_rms_error_curves.ps}
  \caption{Comparison of the $v_\text{rms}$ data with the best fit JAM models.}
  \label{fig:modelB4_vrms}
\end{subfigure}
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
  \caption{Circular velocity curve.}
  \label{fig:modelB4_vcirc}
\end{subfigure}%
\hspace{.02\textwidth}
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_projmass.ps}
  \caption{Enclosed mass profile.}
  \label{fig:modelB4_enclMass}
\end{subfigure}
\caption{Best fit JAM model including a NFW halo and velocity anisotropy with parameters given in Table \ref{tab:modelB4_bestfit}. The 12 lines shown correspond to the 12 models randomly drawn from the posterior probability distribution and marked as grey diamonds in Figure \ref{fig:modelB4_triangle}. Overplotted are the Einstein radius (red dotted line) and the effective half-light radius (black dotted line). The blue dashed line marks the radius within which the data and model were fitted. \emph{Panel a)} shows the comparison of the symmetrized $v_\text{rms}$ data (solid blue points) with the best fit JAM models including a NFW halo (red solid lines). Also shown is the non-symmetrized data at larger radii (open blue dots) and an extrapolation of the best fit models, using the same model parameters but the I-band surface brightness MGE for the outer regions of J1331 derived from the Ellipse model (red dashed lines). \emph{Panel b)} shows the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and dark matter (grey). [TO DO: maybe make one separate circular velocity plot, that also contains the mass-follows-light with Einstein M/L vcirc and compares it with Aaron's vcirc curve.] \emph{Panel c)} shows the corresponding enclosed mass profile. Overplotted is also the Einstein mass at the Einstein radius with a 10\% error, which was used in the fit as an additional constraint.}
\label{fig:modelB4_models}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.7\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
\caption{Generating the rotation curve from the JAM model with NFW halo and constant velocity anisotropy with the mean parameters in Table \ref{tab:modelB4_bestfit} and with the best fit rotation parameter $\kappa' = 0.76$ in Equation \ref{eq:kappa_profile} (red solid lines). The second velocity moment in the first panel and the first velocity moment in the second panel with the additional fit parameter $\kappa'$ were fitted to the symmetrized data (solid blue points). The velocity dispersion is simply $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$. At larger radii we compare the unsymmetrized data (open blue dots), the gas kinematics from \citet{SWELLSV} (green diamonds) and a JAM model using the same model parameters but the light distribution MGE generated from the Ellipse model in Figure \ref{fig:MGEouterRegions} as a prediction for the outer regions of J1331 (red dashed lines). The central regions are very well reproduced and we can also greatly predict the rotation curve at larger radii. Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo.}
\label{fig:modelB4_vrot}
\end{figure*}

### 2015-11-12 archive/v1/docs/results_lensing_v1.02.tex
Started corrections.

\subsection{Mass distribution from Lensing} \label{sec:results_lensing}

\paragraph{Image Positions.} We determine the positions of the lensing images by first subtracting a smooth model for the galaxy's surface brightness from the original image. As models we use MGE fits and IRAF ellipse fits  (see Sections \ref{sec:MGE_theo} and \ref{sec:MGE_results})  to the galaxy in each the F450W and F814W filter. (For example the MGE we use for F814W is the MGE given in Table \ref{tab:MGEF814W} convolved with the PSF in Table \ref{tab:PSFMGEF814W}.) The lensing images become then visible in the residuals (see Figure \ref{fig:lens_just_imgpos}), in which we smooth out noise smaller than the PSF. Because the lensing images are extended, we use the position of the brightest pixel in each of the images. We also use the F450W-MGE subtracted residuals from \citet{SWELLSIII}. The lensing positions as determined from the latter are given in Table \ref{tab:lenspos}. The scatter of lensing positions as determined from subtracting different surface brightness models from the galaxy in different filters gives an error of $\pm 1$ pixel on the image positions. We find slightly different positions for the peak of the surface brightness in the different filters and apply correspondingly an error of one diagonal pixel to the brightness peak in the F450W image which we use as center of the galaxy.
\\Eight image position coordinates allow us to fit a lens mass model with only $<8$ free parameters. We therefore do not fit Fourier components $(a_k,b_k)$ with $k > 3$.
\\Even though the constraints from the image positions on $\alpha$ is very weak, we were however able to show that the image positions in Table \ref{tab:lenspos} are consistent with a model with flat rotation curve. In the following we therefore set $\alpha=1$.

@@

\paragraph{Comparison with Light Distribution.} The surface mass distribution as predicted by the best fit model in Table \ref{tab:bestfitlensmodel} is shown in Figure \ref{fig:lenscomparemass}. We introduced random noise according to the uncertainties in the Fourier shape parameters to create a mock observation that visualizes the effect of the measurement errors. From the mock image's second moment we find an average axis ratio for the lens mass model of $q_\text{lens} \simeq 0.695$, which is consistent with the one found by \citet{SWELLSIII}, $q_\text{lens,SWELLSIII} = 0.67 \pm 0.09$, while the light's average axis ratio in Table \ref{tab:galaxyparameters} is $q' = 0.598$.
\\To estimate the total mass-to-light ratio within the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} = M_\text{ein} / L_\text{I,ein}$, we first integrate the MGE in Table \ref{tab:MGEF814W} to get the total luminosity within the Einstein radius $L_\text{I,ein}$. $L_\text{I,ein}$ and $\Upsilon_\text{I,tot}^\text{ein}$ are given in Table \ref{tab:einsteinML}. $\Upsilon_\text{I,tot}^\text{ein} \sim 5.6$ is consistent or slightly larger than the stellar mass-to-light ratio assuming a Salpeter Initial Mass Function $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ according to \citet{SWELLSI} and Table \ref{tab:previousresults} (see also discussion in Section \ref{sec:MLdiscussion}). We use $\Upsilon_\text{I,tot}^\text{ein}$ to transform the observed surface brightness in the F814W filter into a surface mass density to compare it to the lensing mass distribution (Figure \ref{fig:lenscomparelight}). Figure \ref{fig:lenscompareboth} then compares equidensity contours at the same values of both the predicted lens mass distribution and the observed surface brightness times $\Upsilon_\text{I,tot}^\text{ein}$.
\\Figure \ref{fig:lenslightcompareALL} leads to the following three findings: (1)The mass predicted from lensing and the observed light distribution are oriented in the same direction (i.e. have the same position angle). (2) Within and around the Einstein radius, mass and light distribution have a similar elliptical shape, while further out the mass distribution is slightly rounder. (3) The light distribution drops faster than the mass with increasing radius. Astrophysical reasons for the differences in observed light and measured mass distribution could be, e.g. an apparent change of shape due to dust extinction, a strongly changing $\Upsilon_\text{I,*}$, or the stellar component of the galaxy could be superimposed by a more roundish dark matter component.  We have to note however that the mass distribution is only constraint around the Einstein radius and otherwise an extrapolation.

>>>>

\subsection{Mass distribution from lensing} \label{sec:results_lensing}

\paragraph{Image positions.} We determine the positions of the lensing images by first subtracting a smooth model for the galaxy's surface brightness from the original image. As models we use MGE fits and IRAF ellipse fits  (see Sections \ref{sec:MGE_theo} and \ref{sec:MGE_results})  to the galaxy in each the F450W and F814W filter. (For example the MGE we use for F814W is the MGE given in Table \ref{tab:MGEF814W} convolved with the PSF in Table \ref{tab:PSFMGEF814W}.) The lensing images become then visible in the residuals (see Figure \ref{fig:lens_just_imgpos}), in which we smooth out noise smaller than the PSF. Because the lensing images are extended, we use the position of the brightest pixel in each of the images. We also use the F450W-MGE subtracted residuals from \citet{SWELLSIII}. The lensing positions as determined from the latter are given in Table \ref{tab:lenspos}. The scatter of lensing positions as determined from subtracting different surface brightness models from the galaxy in different filters gives an error of $\pm 1$ pixel on the image positions. We find slightly different positions for the peak of the surface brightness in the different filters and apply correspondingly an error of one diagonal pixel to the brightness peak in the F450W image which we use as center of the galaxy.
\\Eight image position coordinates allow us to fit a lens mass model with only $<8$ free parameters. We therefore do not fit Fourier components $(a_k,b_k)$ with $k > 3$.
\\Even though the constraints from the image positions on $\alpha$ is very weak, we were however able to show that the image positions in Table \ref{tab:lenspos} are consistent with a model with flat rotation curve. In the following we therefore set $\alpha=1$.

@@

\paragraph{Comparison with light distribution.} The surface mass distribution as predicted by the best fit model in Table \ref{tab:bestfitlensmodel} is shown in Figure \ref{fig:lenscomparemass}. We introduced random noise according to the uncertainties in the Fourier shape parameters to create a mock observation that visualizes the effect of the measurement errors. From the mock image's second moment we find an average axis ratio for the lens mass model of $q_\text{lens} \simeq 0.695$, which is consistent with the one found by \citet{SWELLSIII}, $q_\text{lens,SWELLSIII} = 0.67 \pm 0.09$, while the light's average axis ratio in Table \ref{tab:galaxyparameters} is $q' = 0.598$.
\\To estimate the total mass-to-light ratio within the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} = M_\text{ein} / L_\text{I,ein}$, we first integrate the MGE in Table \ref{tab:MGEF814W} to get the total luminosity within the Einstein radius $L_\text{I,ein}$. $L_\text{I,ein}$ and $\Upsilon_\text{I,tot}^\text{ein}$ are given in Table \ref{tab:einsteinML}. $\Upsilon_\text{I,tot}^\text{ein} \sim 5.6$ is consistent or slightly larger than the stellar mass-to-light ratio assuming a Salpeter Initial Mass Function $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ according to \citet{SWELLSI} and Table \ref{tab:previousresults} (see also discussion in Section \ref{sec:MLdiscussion}). We use $\Upsilon_\text{I,tot}^\text{ein}$ to transform the observed surface brightness in the F814W filter into a surface mass density to compare it to the lensing mass distribution (Figure \ref{fig:lenscomparelight}). Figure \ref{fig:lenscompareboth} then compares equidensity contours at the same values of both the predicted lens mass distribution and the observed surface brightness times $\Upsilon_\text{I,tot}^\text{ein}$.
\\Figure \ref{fig:lenslightcompareALL} leads to the following three findings: (1)The mass predicted from lensing and the observed light distribution are oriented in the same direction (i.e. have the same position angle). (2) Within and around the Einstein radius, mass and light distribution have a similar elliptical shape, while further out the mass distribution is slightly rounder. (3) The light distribution drops faster than the mass with increasing radius. Astrophysical reasons for the differences in observed light and measured mass distribution could be, e.g. an apparent change of shape due to dust extinction, a strongly changing $\Upsilon_\text{I,*}$, or the stellar component of the galaxy could be superimposed by a more roundish dark matter component.  We have to note however that the mass distribution is only constraint around the Einstein radius and otherwise an extrapolation.
